The K2 Halo Photometry Campaign

### 2019-04-03 paper/ms.tex
paper updates

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence. For these targets we have provided both long and short cadence reductions.

@@

\begin{figure*}
\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.png}
\end{figure*}

>>>>

\begin{figure*}
\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
\end{figure*}

@@

% short cadence availability 
Seven stars in Campaign~13 and one in Campaign~16 were not only assigned long-cadence halo apertures, but also downloaded at short cadence. For these targets we have provided both long and short cadence reductions. Following the analysis in Section~\ref{optimization} showing the insensitivity of short cadence CDPP to lags longer than $\sim 100$~cad and on choice of objective function, for consistency with  long cadence we have adopted a 300~cadence lag (i.e. $30 \times$ the long cadence lag of 10) and the L1 TV objective function. With their long timeseries the short cadence stars are computationally intractable for the Gaussian Process model in \textsc{k2sc} and we present otherwise uncalibrated halo lightcurves.

@@
